Variational Monte Carlo on bosonic systems

### 2018-03-23 project_1/article/article.tex
Even more on initial results.

@@

	Next we will introduce importance sampling..

>>>>

	In the appendices,  \autoref{fig:initial_problem_b} shows how both the analytic and numeric approach
	matches the exact expression for the energy as a function of $\alpha$ for systems of increasing size. 
	We see also here that the uncertainty increases in the numeric scheme as the system gets larger.

@@

	Next we will introduce importance sampling.
